% ═══════════════════════════════════════════════════════════════════
% Paper 0: Γ-Net Framework — Axioms, Quantities, and Verification
% ═══════════════════════════════════════════════════════════════════
\documentclass[aps,pre,twocolumn,superscriptaddress,floatfix]{revtex4-2}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{xcolor}

\newtheorem{axiom}{Axiom}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

\newcommand{\Aimp}{A_{\text{imp}}}
\newcommand{\Acut}{A_{\text{cut}}}

\begin{document}

\title{$\Gamma$-Net: Minimum Reflection Physics\\
for Dual-Network Life\\[4pt]
\small Framework Definition, Quantity Inventory,\\
and Verification Matrix}

\author{Hsi-Yu Huang}
\email{llc.y.huangll@gmail.com}
\affiliation{Independent Researcher, Taiwan}

\date{\today}

\begin{abstract}
This paper defines the complete axiomatic framework of the
$\Gamma$-Net (\emph{Gamma-Net}) theory: a physics-driven
model of biological organisation based on one variational
principle---Minimum Reflection Action---and three inviolable
constraints C1--C3.
We provide:
(i)~the formal axioms and all derived quantities
($\Gamma$, $A_{\text{imp}}$, $A_{\text{cut}}$,
$D_Z$, $H$, lifecycle ODE, $\Phi_{\text{meta}}$);
(ii)~a unified verification matrix classifying every
prediction as \emph{internal consistency},
\emph{literature-supported}, \emph{NHANES-validated},
or \emph{untested};
(iii)~a falsifiable prediction roadmap for future
experimental work.
The framework unifies phenomena across 15~orders of
magnitude in spatial scale and 29~tissue types under
a single equation: $\Delta Z = -\eta\,\Gamma\,x_{\text{in}}\,x_{\text{out}}$.
This paper contains no new results; it serves as the
master reference for the five companion papers that
develop and test the theory.
\end{abstract}

\maketitle

% ============================================================
%  SECTION 1 — INTRODUCTION
% ============================================================
\section{Introduction: Why This Paper Exists}
\label{sec:intro}

The $\Gamma$-Net framework has been developed across five
companion papers, each deriving a distinct class of
biological phenomena from the Minimum Reflection Principle
(MRP).
Paper~1 derives topology and metabolic scaling~\cite{Paper1};
Paper~2 derives dual neural--vascular organ
health~\cite{Paper2};
Paper~3 derives sleep, the lifecycle equation, and
aging~\cite{Paper3};
Paper~4 derives memory, consciousness, and
nociception~\cite{Paper4};
Paper~5 validates the framework against NHANES
epidemiological data and 29~tissue remodeling
laws~\cite{Paper5}.

A reader entering at any single paper encounters
a local recap of the axioms but lacks:
\begin{enumerate}
  \item a single, canonical list of \emph{all} defined
    quantities and their inter-relations;
  \item a structured table distinguishing which claims
    have external (non-circular) support and which
    remain internal consistency checks;
  \item a roadmap of falsifiable predictions organised
    by experimental modality.
\end{enumerate}
This paper fills those three gaps.
It contains no new derivations or simulations; every result
cited here is proven elsewhere and cross-referenced
to the relevant companion paper.


% ============================================================
%  SECTION 2 — AXIOMS
% ============================================================
\section{The Three Axioms}
\label{sec:axioms}

The theory rests on one variational principle and three
local constraints, labelled \textbf{C1--C3}
(\textbf{C}~$=$~\textbf{Constraint};
the numbering parallels the Three Laws of
Thermodynamics by design).

\subsection{The Minimum Reflection Principle (MRP)}
\label{sec:mrp}

\begin{axiom}[Minimum Reflection Action]
\label{ax:mrp}
Any impedance network subject to sustained energy flow
evolves so as to minimise the total reflected action:
\begin{equation}
  \mathcal{A}[\Gamma]
  = \int_0^T \sum_i \Gamma_i^2(t)\,P_{\text{in},i}(t)\,dt
  \;\to\;\min\,,
  \label{eq:action}
\end{equation}
where $\Gamma_i = (Z_{\text{load},i} - Z_{\text{source},i})
/ (Z_{\text{load},i} + Z_{\text{source},i})$ is the
reflection coefficient at interface~$i$, and
$P_{\text{in},i}$ is the incident power.
\end{axiom}

\noindent
The MRP is not a modelling choice; it is the unique
variational formulation consistent with the First Law of
Thermodynamics at a one-dimensional interface
(Paper~5, Section~2~\cite{Paper5}).

\subsection{C1 --- Energy Conservation}
\label{sec:c1}

\begin{axiom}[C1: Energy Conservation]
\label{ax:c1}
At every interface $i$, at every instant $t$:
\begin{equation}
  \Gamma_i^2(t) + T_i(t) = 1\,,
  \label{eq:c1}
\end{equation}
where $T_i = 1 - \Gamma_i^2$ is the transmission
coefficient (fraction of incident power delivered
to the load).
\end{axiom}

\noindent
C1 is the First Law of Thermodynamics applied locally.
It is not an approximation; it holds exactly for any
lossless interface.  Dissipative corrections (Johnson--Nyquist
noise, Arrhenius aging) modify $Z$ over time but never
violate power balance at a single interface.

\begin{corollary}[Thermal Dissipation]
\label{cor:thermal}
At every interface where $\Gamma_i \neq 0$, the reflected
fraction $\Gamma_i^2$ of incident power is not
``lost''---it is re-absorbed by the source impedance and
ultimately dissipated as Joule heat.
For an organism with $N$ active interfaces, the total
thermal dissipation rate is
\begin{equation}
  P_{\mathrm{heat}} = \sum_{i=1}^{N} \Gamma_i^2\, P_{\mathrm{in},i}\,,
  \label{eq:p-heat}
\end{equation}
where $P_{\mathrm{in},i}$ is the incident power at
interface~$i$.
This heat is not a by-product; it is
the \emph{thermodynamic cost of computation}.
The body temperature~$T_{\mathrm{body}}$ in thermal
steady state satisfies
$P_{\mathrm{heat}} = h A\,(T_{\mathrm{body}} - T_{\mathrm{env}})$,
where $hA$ is the effective thermal conductance to the
environment.  The same impedance mismatches that perform
neural computation therefore \emph{generate the heat
that sustains the temperature at which those computations
remain viable} (Papers~3--4~\cite{Paper3,Paper4}).
\end{corollary}

\subsection{C2 --- Impedance Remodeling}
\label{sec:c2}

\begin{axiom}[C2: Impedance Remodeling]
\label{ax:c2}
The gradient descent of $\mathcal{A}$ with respect to
local impedance yields:
\begin{equation}
  \Delta Z_i = -\eta\,\Gamma_i\,x_{\text{in},i}\,x_{\text{out},i}\,,
  \label{eq:c2}
\end{equation}
where $\eta > 0$ is the remodeling rate,
$x_{\text{in},i}$ is the input signal (effort or flow
arriving at interface~$i$), and
$x_{\text{out},i}$ is the output signal (transmitted
through interface~$i$).
\end{axiom}

\noindent
Equation~\eqref{eq:c2} is the unique local update rule
that decreases $\mathcal{A}$ at every step
(Paper~5, Section~2~\cite{Paper5}).
Its form is identical to Hebb's learning rule when $Z$
is synaptic conductance, to Wolff's law when $Z$ is bone
stiffness, to Glagov's remodeling when $Z$ is vascular
compliance, and to 26~further tissue-specific remodeling
laws (Table~\ref{tab:twentynine}).

\medskip\noindent
\textbf{Historical note.}
In the original formulation (Papers~1--4), C2 was called
the ``Hebbian update'' and its signals were labelled
$x_{\text{pre}}$, $x_{\text{post}}$.
Paper~5 proved that the same equation governs all 
29~tissue types examined, making the neural-specific
terminology misleading.
We adopt the generalised names
\emph{impedance remodeling} and
$(x_{\text{in}}, x_{\text{out}})$ throughout this series.

\subsection{C3 --- Impedance-Tagged Transport}
\label{sec:c3}

\begin{axiom}[C3: Impedance-Tagged Transport]
\label{ax:c3}
Every energy or material flow across an interface carries
$(Z_{\text{source}}, Z_{\text{load}})$ as metadata,
so that $\Gamma_i$ is locally computable without
global network knowledge.
\end{axiom}

\noindent
C3 is a bookkeeping requirement, not an additional
physical law.  It states that whenever a signal crosses
an impedance boundary, the downstream node can compute
$\Gamma$ from local information alone.
In biological terms: blood carries its viscosity
($Z_{\text{blood}}$) into a vessel of compliance
($Z_{\text{vessel}}$); a nerve impulse carries
$R_m + 1/j\omega C_m$ into a synapse of input impedance
$Z_{\text{syn}}$; a mechanical load carries force/velocity
into a bone of stiffness $Z_{\text{bone}}$.

\medskip\noindent
\textbf{Implementation note.}
In the open-source reference implementation (ALICE),
C3 is enforced by requiring all inter-module values to be
\texttt{ElectricalSignal} objects carrying $Z$ metadata.
Raw floating-point numbers between modules are forbidden
at the code level.


% ============================================================
%  SECTION 3 — QUANTITY INVENTORY
% ============================================================
\section{Derived Quantities}
\label{sec:quantities}

Table~\ref{tab:quantities} lists every named quantity
in the $\Gamma$-Net framework, its defining equation,
physical interpretation, and the companion paper where
it first appears.

\begin{table*}[t]
\caption{Complete quantity inventory of the $\Gamma$-Net framework.}
\label{tab:quantities}
\begin{ruledtabular}
\begin{tabular}{llllc}
\textbf{Symbol} & \textbf{Name} & \textbf{Definition} & \textbf{Interpretation} & \textbf{Paper} \\
\hline
$\Gamma_i$ & Reflection coefficient
  & $\frac{Z_{\text{load},i}-Z_{\text{source},i}}{Z_{\text{load},i}+Z_{\text{source},i}}$
  & Mismatch at interface $i$ & 0 \\[4pt]
%
$T_i$ & Transmission coefficient
  & $1 - \Gamma_i^2$
  & Fraction of power delivered & 0 \\[4pt]
%
$\mathcal{A}$ & Reflection action
  & $\int_0^T\!\sum_i \Gamma_i^2 P_{\text{in},i}\,dt$
  & Total wasted energy & 0 \\[4pt]
%
$A_{\text{imp}}$ & Improvable action
  & $\mathcal{A} - A_{\text{cut}}$
  & Reducible by C2 remodeling & 1 \\[4pt]
%
$A_{\text{cut}}$ & Irreducible (cutoff) action
  & $A_{\text{cut}} = \sum_{k>K^*}\!\Gamma_k^2$
  & Topological cost immune to C2 & 1 \\[4pt]
%
$D_Z$ & Impedance debt
  & $\int_0^{T_{\text{wake}}}\!|\Gamma|^2 P_{\text{in}}\,dt$
  & Cumulative mismatch; cleared by sleep & 3 \\[4pt]
%
$D_n,\,D_v$ & Neural / vascular debt
  & $D_Z = D_n + D_v$
  & Dual-network decomposition & 3 \\[4pt]
%
$H$ & Health index
  & $\prod_i(1-\Gamma_i^2)$
  & Whole-body transmission efficiency & 5 \\[4pt]
%
$\Sigma\Gamma^2$ & Total mismatch energy
  & $\sum_i \Gamma_i^2(t)$
  & Instantaneous network mismatch & 3 \\[4pt]
%
\multirow{2}{*}{Lifecycle ODE} & \multirow{2}{*}{Lifecycle equation}
  & $\frac{d(\Sigma\Gamma^2)}{dt} = -\eta\,\Sigma\Gamma^2$
  & \multirow{2}{*}{Cognition bathtub curve} & \multirow{2}{*}{3} \\
  & & $\;+\gamma\,\Gamma_{\text{env}} + \delta\,D(t)$  & & \\[4pt]
%
$\Phi_{\text{meta}}$ & Meta-reflection coefficient
  & $\frac{Z_{\text{obs}}-Z_{\text{act}}}{Z_{\text{obs}}+Z_{\text{act}}}$
  & Self-monitoring; consciousness marker & 4 \\[4pt]
%
$\mathcal{S}$ & Null space (``soul'')
  & $\ker(\partial Z / \partial t)$
  & Impedances immune to all experience & 4 \\[4pt]
%
$\beta$ & Murray bifurcation ratio
  & $2^{1/3} \approx 1.26$
  & Optimal branch radius ratio & 1 \\[4pt]
%
$\Omega$ & Dual-network overhead
  & $\ge 1$
  & Packing cost of two trees in one volume & 1 \\
\end{tabular}
\end{ruledtabular}
\end{table*}


% ============================================================
%  SECTION 4 — SERIES MAP
% ============================================================
\section{Series Architecture}
\label{sec:series}

The five companion papers form a logical chain:

\begin{enumerate}
  \item \textbf{Paper~1: Topology and Fractal Cost}~\cite{Paper1}.
    Proves the irreducibility theorem
    ($\mathcal{A} = A_{\text{imp}} + A_{\text{cut}}$,
    $A_{\text{cut}} > 0$), derives relay-node hierarchies,
    the Murray bifurcation ratio $\beta = 2^{1/3}$,
    Kleiber's 3/4-power metabolic scaling, joint impedance
    transformers, and dual-network packing overhead~$\Omega$.

  \item \textbf{Paper~2: Dual-Network Organ Health}~\cite{Paper2}.
    Applies MRP to vascular networks; derives Murray's law
    from $\Gamma$-minimisation; defines the dual-network
    health index $H = (1-\Gamma_n^2)(1-\Gamma_v^2)$;
    models five vascular diseases as impedance failure modes.
    Validated against 12/12 published clinical benchmarks with
    100\% pass rate.

  \item \textbf{Paper~3: Temporal Dynamics}~\cite{Paper3}.
    Introduces impedance debt $D_Z$; derives sleep as
    $D_Z$-discharge; derives the lifecycle equation governing
    cognition from birth to death; models emotion as
    $\Gamma$-dynamics readout; derives aging as Arrhenius
    fatigue; explains aging pain immunity via slow $Z$-drift.

  \item \textbf{Paper~4: Memory, Consciousness, Nociception}~\cite{Paper4}.
    Defines memory as $dZ/dt$, consciousness as closed-loop
    $\Phi_{\text{meta}}$, and the null space $\mathcal{S}$
    (``soul'') as $\ker(\partial Z/\partial t)$.
    Proves the Television Theorem distinguishing open-loop
    from closed-loop systems.

  \item \textbf{Paper~5: Clinical Validation}~\cite{Paper5}.
    Proves C2 governs all 29~tissue types (not just neurons);
    validates against NHANES ($n = 49{,}774$, zero fitted
    parameters, 7/7~organs significant);
    reports all-cause mortality $C = 0.70$,
    Q1-vs-Q4 risk ratio $= 6.89\times$;
    provides sex-as-boundary-condition analysis.
\end{enumerate}

\noindent
Papers~1--4 are primarily theoretical with internal
computational verification.
Paper~5 breaks the circularity with external epidemiological
data.


% ============================================================
%  SECTION 5 — VERIFICATION MATRIX
% ============================================================
\section{Verification and Validation Matrix}
\label{sec:vv}

Table~\ref{tab:vv} classifies every major claim by its
current evidence status.
Four levels are used:

\begin{description}
  \item[IC] \textbf{Internal consistency.}
    Verified within the ALICE simulation engine.
    Self-confirming; does not constitute independent evidence.
  \item[LIT] \textbf{Literature-supported.}
    Prediction matches published experimental or clinical
    data not used in model construction.
  \item[EXT] \textbf{Externally validated.}
    Tested against independent dataset (NHANES) with
    zero fitted parameters and hash-locked predictions.
  \item[UT] \textbf{Untested.}
    Falsifiable prediction not yet confronted with data.
\end{description}

\begin{table*}[t]
\caption{Verification and validation matrix.
IC = internal consistency;
LIT = literature-supported;
EXT = externally validated (NHANES);
UT = untested prediction.}
\label{tab:vv}
\begin{ruledtabular}
\begin{tabular}{llcccc}
\textbf{Claim} & \textbf{Paper} & \textbf{IC} & \textbf{LIT} & \textbf{EXT} & \textbf{UT} \\
\hline
\multicolumn{6}{l}{\textit{Topology and scaling (Paper~1)}} \\
Relay nodes emerge from MRP & 1 & $\checkmark$ & & & \\
$\tau_{\text{conv}} \propto N^{-0.46}$ & 1 & $\checkmark$ & & & \\
$A_{\text{cut}} > 0$ (irreducibility) & 1 & $\checkmark$ & & & \\
Murray ratio $\beta = 2^{1/3}$ & 1 & $\checkmark$ & $\checkmark$ & & \\
Kleiber's law $B \propto M^{3/4}$ & 1 & $\checkmark$ & $\checkmark$ & & \\
Joint = quarter-wave transformer & 1 & $\checkmark$ & & & $\checkmark$ \\
$A_{\text{cut}} \propto M^{2/3}$ & 1 & $\checkmark$ & $\checkmark$ & & \\
\hline
\multicolumn{6}{l}{\textit{Dual-network organ health (Paper~2)}} \\
Murray's law from $\Gamma$-minimisation & 2 & $\checkmark$ & $\checkmark$ & & \\
Dual-network health $H=(1{-}\Gamma_n^2)(1{-}\Gamma_v^2)$ & 2 & $\checkmark$ & & $\checkmark$ & \\
Vascular disease as $Z$-mismatch & 2 & $\checkmark$ & $\checkmark$ & & \\
12/12 clinical calibration tests & 2 & & $\checkmark$ & & \\
\hline
\multicolumn{6}{l}{\textit{Temporal dynamics (Paper~3)}} \\
Sleep = $D_Z$ discharge & 3 & $\checkmark$ & $\checkmark$ & & \\
Jellyfish sleep without brain & 3 & & $\checkmark$ & & \\
Brain required for thermal management & 3 & $\checkmark$ & $\checkmark$ & & \\
Lifecycle bathtub curve & 3 & $\checkmark$ & $\checkmark$ & & \\
Yerkes--Dodson as impedance optimum & 3 & $\checkmark$ & $\checkmark$ & & \\
Aging = Arrhenius fatigue on $Z$ & 3 & $\checkmark$ & & & \\
Aging pain immunity (slow drift) & 3 & $\checkmark$ & & & $\checkmark$ \\
Infant sleep duration vs $D_Z$ & 3 & $\checkmark$ & $\checkmark$ & & \\
\hline
\multicolumn{6}{l}{\textit{Memory, consciousness, nociception (Paper~4)}} \\
Memory = $dZ/dt$ & 4 & $\checkmark$ & & & \\
$\Phi_{\text{meta}}$ as consciousness marker & 4 & $\checkmark$ & & & $\checkmark$ \\
Null space $\mathcal{S} = \ker(\partial Z/\partial t)$ & 4 & $\checkmark$ & & & \\
Television Theorem (open/closed loop) & 4 & $\checkmark$ & & & $\checkmark$ \\
Thermal hierarchy: PFC fails before V1 & 4 & $\checkmark$ & $\checkmark$ & & $\checkmark$ \\
\hline
\multicolumn{6}{l}{\textit{Clinical validation (Paper~5)}} \\
C2 = 29 tissue remodeling laws & 5 & & $\checkmark$ & & \\
NHANES 7/7 organ AUC significant & 5 & & & $\checkmark$ & \\
Endocrine AUC = 0.823 & 5 & & & $\checkmark$ & \\
All-cause mortality $C = 0.70$ & 5 & & & $\checkmark$ & \\
Q1 vs Q4 mortality ratio = $6.89\times$ & 5 & & & $\checkmark$ & \\
Sex as boundary condition on $Z_{\text{setpoint}}$ & 5 & & $\checkmark$ & $\checkmark$ & \\
Cardiac AUC gain $+0.166$ from vascular input & 5 & & & $\checkmark$ & \\
$H$ decreases with disease burden ($\rho = -0.378$) & 5 & & & $\checkmark$ & \\
\end{tabular}
\end{ruledtabular}
\end{table*}


% ============================================================
%  SECTION 6 — PREDICTION ROADMAP
% ============================================================
\section{Prediction Roadmap}
\label{sec:roadmap}

Table~\ref{tab:predictions} organises the falsifiable
predictions of the $\Gamma$-Net framework by experimental
modality, enabling independent groups to test specific
claims without needing the full simulation engine.

\begin{table*}[t]
\caption{Falsifiable prediction roadmap.
Each prediction is testable with existing technology.}
\label{tab:predictions}
\begin{ruledtabular}
\begin{tabular}{lllc}
\textbf{Domain} & \textbf{Prediction} & \textbf{Method} & \textbf{Paper} \\
\hline
\multicolumn{4}{l}{\textit{Physiological}} \\
& PFC fails before V1 under hyperthermia
  & Controlled heating + fMRI/EEG & 4 \\
& Vascular $\Gamma$ correlates with PWV / elastography
  & BIS + arterial tonometry & 2 \\
& Joint cartilage $\approx$ quarter-wave transformer
  & Ultrasound impedance spectroscopy & 1 \\
& Bone-on-bone OA raises local $\Gamma^2$ measurably
  & Intra-articular force sensors & 1 \\
\hline
\multicolumn{4}{l}{\textit{Sleep \& circadian}} \\
& Cross-species $D_{\text{thermal}}/D_{\text{micro}}$ ratio
  predicts NREM/REM partition
  & Polysomnography + metabolic calorimetry & 3 \\
& Sleep rebound magnitude $\propto$ wake-duration $D_Z$
  & EEG slow-wave power after controlled deprivation & 3 \\
& Jellyfish sleep duration scales with $\kappa_{\text{eff}}$
  & Temperature-controlled aquarium experiments & 3 \\
\hline
\multicolumn{4}{l}{\textit{Cognitive / developmental}} \\
& Infantile amnesia offset tracks myelination Z-change
  & Retrospective longitudinal EEG + structural MRI & 3 \\
& Yerkes--Dodson peak shifts with $\eta$ (skill level)
  & Psychophysics + cortisol monitoring & 3 \\
& Aging pain immunity: slow $Z$-drift below pain threshold
  & Quantitative sensory testing, longitudinal & 3 \\
\hline
\multicolumn{4}{l}{\textit{Clinical / epidemiological}} \\
& $\Gamma$-vector predicts disease in non-US populations
  & NHANES-equivalent cohorts (UK Biobank, Taiwan MJ) & 5 \\
& $H$ predicts surgical outcome / length of stay
  & Prospective peri-operative cohort & 5 \\
& Network propagation: renal $\Gamma$ predicts cardiac events
  & Longitudinal cardiorenal registry & 5 \\
\hline
\multicolumn{4}{l}{\textit{Thermoregulation / comparative}} \\
& $T_c(K)$: no high-$K$ organism sustained below $T_c$ with cognition
  & Comparative physiology database + torpor EEG & 1 \\
& Hibernation EEG power scales with $K \cdot \Gamma^2(T)$
  & Cross-species torpor polysomnography & 1 \\
& Nocturnal shelter-seeking scales with $K$
  & Comparative ethology $\times$ thermoregulation data & 1 \\
\end{tabular}
\end{ruledtabular}
\end{table*}


% ============================================================
%  SECTION 7 — INTERFACE SCALE TABLE (SUMMARY)
% ============================================================
\section{The Interface Scale Table}
\label{sec:scales}

The same equation ($\Gamma$, C1, C2) applies across seven
distinct physical domains and 14~orders of magnitude in
spatial scale:

\begin{table}[h]
\caption{Representative interfaces grouped by physical domain.
Full table with impedance definitions: Paper~5~\cite{Paper5}.}
\label{tab:scales}
\begin{ruledtabular}
\begin{tabular}{llc}
\textbf{Domain} & \textbf{Interface} & \textbf{Scale} \\
\hline
Electrical   & Synapse / ion channel       & 25\,nm--1\,$\mu$m \\
Electrical   & Power-grid transformer      & 10\,m \\
Hydraulic    & Arteriole (Poiseuille)      & 100\,$\mu$m \\
Hydraulic    & Whole-body vascular         & 1\,m \\
Acoustic     & Tissue boundary (ultrasound)& 1\,mm \\
Acoustic     & Submarine hull              & 10\,m \\
Electromagnetic & Optical fibre splice     & 100\,$\mu$m \\
Electromagnetic & Ionospheric waveguide    & $10^6$\,m \\
Mechanical   & Bone--cartilage joint       & 10\,cm \\
Mechanical   & Tendon--muscle junction     & 1\,cm \\
Thermal      & Brain thermal boundary      & 10\,cm \\
Thermal      & Skin--air interface         & 1\,m \\
Chemical     & Organ parenchyma            & 10\,cm \\
\end{tabular}
\end{ruledtabular}
\end{table}

\noindent
At every scale, the physics is identical: only the
definition of $Z$ changes (electrical, acoustic,
mechanical, hydraulic, thermal, electromagnetic,
chemical).
The universality is not an analogy; it is the same
theorem applied to different media.

Moreover, every row in the table participates in the same
closed loop: \textbf{perception}
($x_{\text{in}}$ measurement) $\to$
\textbf{error} ($\Gamma$ mismatch) $\to$
\textbf{compensation} (C2: $\Delta Z =
-\eta\,\Gamma\,x_{\text{in}}\,x_{\text{out}}$) $\to$
\textbf{re-perception} (updated $\Gamma'$ and
$x_{\text{in}}'$).
This perception--compensation cycle is the operational
meaning of C1--C2 at every interface; Paper~5
elaborates it across all seven domains.


% ============================================================
%  SECTION 8 — TWENTY-NINE TISSUES (SUMMARY TABLE)
% ============================================================
\section{The Twenty-Nine C2 Networks}
\label{sec:twentynine}

Paper~5 proves that C2 (Eq.~\ref{eq:c2}) recovers 29
independently discovered tissue-remodeling laws when the
generic signals $(x_{\text{in}}, x_{\text{out}})$ are
identified with tissue-specific physical quantities.
Table~\ref{tab:twentynine} provides the mapping.

\begin{table*}[t]
\caption{The 29 $\Gamma$-networks.
Each row maps C2 to a known remodeling law by identifying
$x_{\text{in}}$, $x_{\text{out}}$, and $Z$.
Full derivations: Paper~5~\cite{Paper5}.}
\label{tab:twentynine}
\begin{ruledtabular}
\begin{tabular}{lllll}
\textbf{Tissue} & \textbf{Known law}
  & $x_{\text{in}}$ & $x_{\text{out}}$ & $Z$ \textbf{definition} \\
\hline
Neural        & Hebb's law (1949)              & Pre-synaptic spike & Post-synaptic EPSP & $R_m + 1/j\omega C_m$ \\
Vascular      & Glagov remodeling (1987)       & Wall shear stress  & Endothelial response & $P/Q$ (Poiseuille) \\
Skeletal      & Wolff's law (1892)             & Applied load       & Bone strain        & Force/velocity \\
Muscular      & Davis's law (1867)             & Neural drive       & Muscle tension     & Stiffness \\
Immune        & Clonal selection               & Antigen (APC)      & T/B cell activation & Receptor affinity \\
Epithelial    & Keratinisation                 & External friction  & Tissue deformation & Thermal+mechanical $Z$ \\
Pulmonary     & Altitude acclimatisation       & Ventilation demand & Alveolar expansion & $P_{\text{aw}}/\dot{V}$ \\
GI tract      & Intestinal adaptation          & Luminal content    & Epithelial uptake  & Absorption $Z$ \\
Endocrine     & Receptor regulation            & Hormone conc.      & Intracellular resp.& $1/K_d$ \\
Lymphatic     & Reactive hypertrophy           & Tissue load        & Lymph node response& Drainage $Z$ \\
Renal         & TG feedback                    & Macula densa signal& Arteriolar response& $P_{\text{glom}}/Q_{\text{filt}}$ \\
Hepatic       & Liver regeneration             & Portal HGF         & Hepatocyte prolif. & Clearance $Z$ \\
Connective    & Tendon remodeling              & Mechanical strain  & Fibroblast response& $EA/L$ \\
Adipose       & Leptin signaling               & Insulin signal     & Adipocyte response & Storage $Z$ \\
Hematopoietic & Erythropoiesis                 & EPO signal         & Erythroid response & $P_{O_2}/Q_{O_2}$ \\
Reproductive  & Follicular selection           & Gonadotropin       & Granulosa/germ cell& $1/(N_R K_a)$ \\
Cardiac       & Laplace--Starling              & Wall stress $\sigma$ & Myocardial strain $\varepsilon$ & Chamber compliance \\
Brain (reg.)  & Baroreflex resetting           & Sensory afferent   & Motor efferent     & Controller gain \\
Ocular        & IOP homeostasis                & Aqueous pressure   & Trabecular drainage& $P_{\text{IOP}}/Q_{\text{aq}}$ \\
Auditory      & Tonotopic plasticity           & Sound pressure     & Hair cell response & Cochlear $Z$ \\
Vestibular    & VOR adaptation                 & Angular velocity   & Oculomotor response& Vestibular gain \\
Olfactory     & Receptor turnover              & Odorant conc.      & ORN response       & Receptor $1/K_d$ \\
Dental        & Tertiary dentinogenesis        & Thermal/mech.\ insult & Odontoblast resp.& Dentin $Z$ \\
Enteric       & Enteric plasticity             & Luminal distension & ENS firing         & Gut wall compliance \\
Autonomic     & Sympathovagal remod.           & Baroreceptor input & Effector output    & Sympathovagal $Z$ \\
Pancreatic    & $\beta$-cell compensation      & Glucose load       & Insulin secretion  & $1/(N_\beta \cdot k_{\text{sec}})$ \\
CSF           & Choroid regulation             & CSF pressure       & Production rate    & $P_{\text{CSF}}/Q_{\text{CSF}}$ \\
Brain (func.) & Cortical map plasticity        & Afferent frequency & Cortical area      & Synaptic $Z$ matrix \\
Cartilage     & \textit{C2 null} ($\eta\approx 0$) & Mechanical load & (negligible)       & $H_A A/h$ \\
\end{tabular}
\end{ruledtabular}
\end{table*}


% ============================================================
%  SECTION 9 — TISSUE BLUEPRINTS
% ============================================================
\section{Tissue Blueprints: From Table to Topology}
\label{sec:blueprints}

Table~\ref{tab:twentynine} maps C2 to 29~remodeling laws,
but it does not specify \emph{how} those tissues are
physically wired.
This section defines \emph{tissue blueprints}: concrete
\texttt{GammaTopology} instances in which every node is a
\texttt{GammaNode} with a biologically assigned mode count~$K$,
and every edge is a \texttt{MulticoreChannel} enforcing C1/C2/C3
at each tick.

A blueprint contains:
\begin{enumerate}
  \item A set of $\texttt{GammaNode}$s with tissue-appropriate
    $\texttt{TissueType}$ (which sets~$K$, $Z_{\text{mean}}$,
    and myelination).
  \item A wiring diagram: directed edges
    $(\text{source}, \text{target})$.
  \item A factory function returning a ready-to-run
    \texttt{GammaTopology}.
\end{enumerate}

\noindent
Diseases are \emph{not coded} in the blueprint.
Disease $=$ perturbation of initial conditions
(impedance shift, edge removal, or stimulus pattern)
applied to a healthy blueprint, then evolved via
\texttt{GammaTopology.tick()}.

\subsection{Cardiovascular blueprint}

Eleven nodes span four $K$-levels:

\begin{center}
\begin{tabular}{llc}
\hline
\textbf{Node} & \textbf{TissueType} & $K$ \\
\hline
SA node, AV node, LV, RV,         & Cardiac Purkinje      & 4 \\
\quad aortic valve, pulm.\ valve,  &                       &   \\
\quad aorta, coronary              &                       &   \\
Arterioles                          & Vasc.\ smooth muscle  & 2 \\
Pulmonary artery                    & Autonomic preganglionic & 2 \\
Capillaries                         & Endothelial           & 1 \\
\hline
\end{tabular}
\end{center}

Fourteen directed edges connect the conduction system
(SA$\to$AV$\to$LV/RV), left-heart systemic path
(LV$\to$valve$\to$aorta$\to$coronary/arterioles$\to$capillaries),
right-heart pulmonary path, and return paths.
The dimensional cascade $K{=}4 \to 2 \to 1$ guarantees
$\Acut > 0$ (Paper~1 irreducibility theorem),
physically representing the loss of pulsatile modes as
blood flows from elastic arteries to resistance vessels.

\subsection{Neural blueprint}

Nine nodes span four $K$-levels:

\begin{center}
\begin{tabular}{llc}
\hline
\textbf{Node} & \textbf{TissueType} & $K$ \\
\hline
Cortex (motor, sensory), thalamus  & Cortical pyramidal    & 5 \\
Spinal (motor, sensory),           & Motor $\alpha$ / Sensory A$\beta$  & 3 \\
\quad motor neuron, sensory neuron &                       &   \\
Nociceptor A$\delta$               & Pain A$\delta$ fibre  & 2 \\
Nociceptor C                       & Pain C fibre          & 1 \\
\hline
\end{tabular}
\end{center}

Twelve directed edges form descending motor
(cortex$\to$thalamus$\to$spinal$\to$motor neuron),
ascending sensory
(sensory neuron$\to$spinal$\to$thalamus$\to$cortex),
pain pathway
(C fibre$\to$A$\delta$$\to$spinal),
and sensorimotor cross-connections.
The cascade $K{=}5 \to 3 \to 2 \to 1$ defines
the \emph{neural cable degradation spectrum}:
\begin{center}
\begin{tabular}{cl}
\hline
$\Gamma$ & \textbf{Clinical correlate} \\
\hline
$\approx 0.0$ & Normal conduction (healthy match) \\
$\approx 0.1$ & Fever, neuroinflammation (thermal noise $\uparrow$) \\
$\approx 0.3$ & PTSD (structurally locked $\varepsilon$; dormant until triggered, Paper~4, Sec.~7.10) \\
$\approx 0.7$ & ALS (progressive channel collapse) \\
$\to 1.0$     & Phantom limb pain (open-circuit echo) \\
\hline
\end{tabular}
\end{center}

\noindent
These are not disease models; they are predictions of what
$\Gamma$-values \emph{should} emerge from topology perturbations
alone.
Paper~1 verifies the topology-level physics;
Paper~5 verifies the disease-level emergence.

\subsection{Complete tissue atlas}
\label{sec:tissue-atlas}

The cardiovascular and neural blueprints above are two of
29~organ-system blueprints implemented in
\texttt{BLUEPRINT\_REGISTRY}.
Table~\ref{tab:atlas} lists all 29, totalling
$\sim\!217$~nodes and $\sim\!242$~directed edges.
Every blueprint passes C1 energy conservation at every edge
and C2 physics verification ($\Aimp$~non-increasing,
$\Acut$~invariant) under 100~ticks of evolution.

\begin{table}[h]
\caption{\label{tab:atlas}Complete tissue blueprint atlas.
Nodes~($N$), edges~($E$), and mode count range are listed
for each organ system.}
\begin{ruledtabular}
\begin{tabular}{llccl}
\textbf{System} & $N$ & $E$ & $K$-range & \textbf{Key feature} \\
\hline
Cardiovascular   & 11 & 13 & 1--4 & Pulsatile cascade \\
Neural           &  9 & 11 & 1--5 & Cable degradation \\
Pulmonary        &  7 &  7 & 1--3 & Gas exchange \\
Renal            &  9 &  9 & 1--3 & TG feedback \\
Hepatic          &  7 &  7 & 1--3 & Dual blood supply \\
Gastrointestinal &  8 & 10 & 1--3 & Mucosal barrier \\
Endocrine        &  8 & 11 & 1--3 & Negative feedback \\
Immune           &  7 &  9 & 1--3 & Innate/adaptive \\
Lymphatic        &  7 &  7 & 1--2 & One-way drainage \\
Musculoskeletal  &  7 &  8 & 1--3 & Motor unit \\
Skeletal         &  6 &  7 & 1--2 & Wolff's law \\
Epithelial       &  8 &  8 & 1--2 & Barrier layers \\
Connective       &  6 &  6 & 1--2 & ECM turnover \\
Adipose          &  6 &  7 & 1--2 & Metabolic storage \\
Hematopoietic    &  9 &  9 & 1--3 & EPO feedback \\
Cartilage        &  4 &  4 & 1   & $\eta \approx 0$ (avascular) \\
Reproductive     &  6 &  7 & 1--2 & Hormonal axis \\
Brain regulatory &  7 &  8 & 2--3 & Autonomic control \\
Vascular         & 11 & 11 & 1--3 & Arterial tree \\
Ocular           &  9 &  9 & 1--3 & IOP regulation \\
Auditory         &  7 &  7 & 1--3 & Tonotopic cascade \\
Vestibular       &  6 &  6 & 1--2 & Balance loops \\
Olfactory        &  4 &  4 & 1   & Receptor turnover \\
Dental           &  7 &  7 & 1--2 & Pulp--dentin axis \\
Enteric          &  7 &  7 & 1--3 & Gut nervous system \\
Autonomic        &  8 & 10 & 1--3 & Sympathetic/para \\
Pancreatic       &  7 &  8 & 1--2 & Paracrine islet \\
CSF              &  8 &  8 & 1--2 & Choroid--ventricle \\
Brain functional & 12 & 21 & 3--5 & Cortex--subcortex \\
\end{tabular}
\end{ruledtabular}
\end{table}

\noindent
Cartilage ($\eta \approx 0.001$) and olfactory receptors ($K = 1$)
represent the extremes: cartilage barely remodels (avascular),
while olfactory neurons are among the few that regenerate
throughout life.
Brain functional topology has the richest dimensional structure
($K = 5$ cortex vs.\ $K = 3$ subcortex, 21~edges),
producing the highest $\Acut$ of any blueprint.

\subsection{Whole-body inter-organ topology}
\label{sec:whole-body}

The 29~blueprints above are \emph{intra}-organ networks.
A living body also requires \emph{inter}-organ communication:
every organ receives arterial blood supply (vascular bus)
and autonomic innervation (neural bus), and the brain
serves as a central command hub.

We unify the three chains into a single
\texttt{GammaTopology} via \texttt{build\_whole\_body()}:

\begin{enumerate}
  \item \textbf{Organ layer:} all 29~blueprints are
    instantiated with prefixed node names
    (e.g.\ \texttt{cv.sa\_node}, \texttt{pulm.alveolus}).
  \item \textbf{Vascular bus:} an aortic trunk node ($K = 4$)
    fans out to 29~arteriolar branch nodes ($K = 2$),
    each connecting to the organ's designated vascular
    interface node.  K-cascade: $4 \to 2 \to K_{\text{organ}}$.
  \item \textbf{Neural bus:} an autonomic trunk node ($K = 3$)
    fans out to 29~branch nodes ($K = 2$),
    each connecting to the organ's neural interface node.
    K-cascade: $3 \to 2 \to K_{\text{organ}}$.
  \item \textbf{Brain hub:} the brain\_functional blueprint's
    \texttt{hypothalamus\_b} ($K{=}3$) drives the neural bus
    trunk (descending command),
    while the vascular bus feeds back to the brain
    (interoception).
\end{enumerate}

\noindent
The resulting whole-body graph contains
\textbf{278~nodes} and \textbf{426~directed edges},
with $K$ spanning 1 to~5.
All edges satisfy C1 ($\Gamma^2 + T = 1$) by construction.
The vascular bus contributes $\Acut = 2$ at every
trunk-to-branch edge ($K{=}4 \to K{=}2$),
the neural bus contributes $\Acut = 1$ ($K{=}3 \to K{=}2$),
and further cutoff costs accumulate at every bus-to-organ
junction.
The total structural action $\Acut = 222$ is irreducible
under all C2~gradients---it is the geometric price
of multi-organ life.

Disease cascades emerge automatically from this topology:
raising the aortic impedance (vascular stenosis) increases
$\Gamma$ at all downstream branches, which propagates via
the bus to every organ's vascular interface.
No disease-specific code is needed (E0).
The 145~whole-body tests (\texttt{tests/test\_whole\_body.py})
verify structure, C1/C2 physics, bus connectivity,
dimensional cascade, signal propagation, and
reproducibility.

\subsection{Thermoregulation as a \texorpdfstring{$\Gamma$}{Gamma}-Net necessity}
\label{sec:thermoregulation}

Blood is the transmission medium of the vascular bus.
Its viscosity $\eta$ depends on body temperature $T$ via
the Arrhenius relation:
\begin{equation}\label{eq:arrhenius-eta}
  \tilde\eta(T)
  \;=\;
  \exp\!\Bigl[\alpha\Bigl(\frac{1}{T}-\frac{1}{T_0}\Bigr)\Bigr],
  \qquad
  \alpha \equiv \frac{E_a}{R} \approx 1949\;\text{K},
\end{equation}
where $E_a \approx 16.2$~kJ\,mol$^{-1}$ is the activation energy
for viscous flow in plasma and $T_0 = 310$~K ($37\,^\circ$C).
In the Poiseuille limit, the vascular bus impedance
$Z_{\text{bus}}(T) = Z_{\text{ref}}\,\tilde\eta(T)$.
At every organ--bus junction the reflection coefficient becomes
\begin{equation}
  \Gamma_i(T)
  \;=\;
  \frac{Z_{\text{organ},i} - Z_{\text{bus}}(T)}
       {Z_{\text{organ},i} + Z_{\text{bus}}(T)}\,,
\end{equation}
and the vascular contribution to the whole-body action is
$A_{\text{vasc}}(T) = \sum_i K_{\text{common},i}\,\Gamma_i^2(T)$.

C2 repair runs at a rate that is itself temperature-dependent
(enzymatic Arrhenius,
$\tilde\eta_{\text{learn}}(T) = \exp[\beta(T_0^{-1}-T^{-1})]$
with $\beta = E_{\text{learn}}/R \approx 6015$~K).
The repair time therefore scales as
\begin{equation}\label{eq:tau-doubly}
  \tilde\tau(T)
  \;=\;
  \frac{\tilde\eta(T)}{\tilde\eta_{\text{learn}}(T)}
  \;=\;
  \exp\!\Bigl[(\alpha+\beta)\Bigl(\frac{1}{T}-\frac{1}{T_0}\Bigr)\Bigr],
\end{equation}
which is \emph{doubly exponential} in $1/T$:
viscosity rises while repair rate falls.

Setting $\tilde\tau(T_c) = \tau_{\max}$ yields the
\textbf{critical temperature}
\begin{equation}\label{eq:Tc}
  T_c
  \;=\;
  \frac{T_0}{1 + \dfrac{T_0\,\ln\tau_{\max}}{\alpha+\beta}}\,.
\end{equation}
For an organism with brain modal complexity~$K$,
the action scales as $K\,\Gamma^2$, so the effective
$\tau_{\max}$ shrinks by~$1/K$, giving
$T_c(K) > T_c(1)$ for $K > 1$ (dimensional amplification).
The 93~thermoregulation tests confirm:

\begin{center}
\begin{tabular}{rl}
  $T_c(K{=}1)$ & $= -10.3\,^\circ$C  (ectotherm viable) \\
  $T_c(K{=}5)$ & $= +4.5\,^\circ$C   (endothermy required) \\
\end{tabular}
\end{center}

\noindent
Higher~$K$ brains \emph{must} maintain $T > T_c(K)$,
rendering endothermy a necessary condition for complex
neural topology---not a metabolic luxury but a
$\Gamma$-topological constraint.

\paragraph{Thermodynamic boundary crisis during
$D_Z$ clearance.}
To discharge accumulated impedance debt~$D_Z$
(Paper~3~\cite{Paper3}), the system must enter a
low-power state (sleep), reducing metabolic heat
generation to a basal level~$P_{\text{basal}}$.
System temperature during sleep obeys
\begin{equation}
  T_{\text{sys}}
  = T_{\text{env}} + P_{\text{basal}}\,R_{\text{th}}\,,
  \label{eq:T-sleep}
\end{equation}
where $R_{\text{th}}$ is the organism's effective thermal
resistance (integrating fur, blubber, posture, and
huddling---all abstracted as a single lumped parameter).
The C2 boundary condition demands
$T_{\text{sys}} > T_c(K)$ at all times;
violation halts remodelling and freezes impedance
mismatch in place.

During nocturnal or seasonal temperature drops,
$T_{\text{env}}$ may swing by tens of kelvin.
When $P_{\text{basal}}\,R_{\text{th}}$ alone cannot
guarantee the inequality, the organism must couple to
an \emph{environmental thermal low-pass filter}---any
high-heat-capacity mass (subterranean rock, tree
hollows, snow caves, or conspecific huddles) whose
thermal inertia damps the external oscillation:
\begin{equation}
  T_{\text{refugium}}(z)
  \approx \overline{T}_{\text{annual}}\,,
  \qquad z \gg \delta
  = \sqrt{2\kappa/(\rho c_p\,\omega)}\,,
  \label{eq:thermal-LPF}
\end{equation}
where $\delta$ is the thermal penetration depth.
Ecologically, such environments are called
\emph{thermal refugia}; physically, they are low-pass
filters that replace the volatile $T_{\text{env}}$ with
a stable baseline~$\overline{T}_{\text{annual}}$.

The resulting constraint chain is purely physical:
high~$K$ $\to$ high~$T_c(K)$ $\to$
sleep reduces $P_{\text{met}}$ $\to$
$P_{\text{basal}}\,R_{\text{th}}$ may be insufficient
$\to$ external thermal coupling required.
Low-$K$ organisms ($T_c \ll 0\,^\circ$C) satisfy the
inequality with biological insulation alone and need
no refugium.

\paragraph{Falsification criterion.}
The $T_c(K)$ formula is falsified by exhibiting an organism with
(i)~closed high-pressure vasculature,
(ii)~$K \geq 5$,
(iii)~sustained $T_{\text{body}} \leq T_c(K)$, and
(iv)~maintained high-level cognition.
No such organism is currently known.
Mammalian hibernators drop $T$ below $T_c$ but simultaneously
reduce brain activity to torpor~\cite{PMC6674705,PMC6629779};
ectotherms with complex behaviour operate on the low-$K$ branch
where $T_c$ is low~\cite{PMC11880559};
cross-vertebrate data confirm that species with higher, more
stable body temperatures develop larger brains at given body
mass~\cite{PMC12625846,PMC7907648}.

\paragraph{Gating, ``willpower,'' and time perception.}
The preceding analysis explains winter lethargy
as a minimum-action consequence: at low~$T$,
$\Gamma^2$ rises on every channel, and the cheapest
response is quiescence---close thalamic gates
($G_i \to 0$; see the television inequality,
Paper~4~\cite{Paper4}) and reduce the summation
$A = \sum_i K_i\,\Gamma_i^2\,P_{\mathrm{in},i}$.
This is the physics behind ``not wanting to move in winter.''

Yet organisms override it.  The mechanism is
\emph{bandwidth reallocation under a fixed thermal
ceiling}~$P_{\max}$.
By closing $N-1$ thalamic gates the prefrontal cortex
receives only one stream; its full processing quality
$Q_{\text{PFC}}$ and bandwidth~$B_{\text{PFC}}$
are devoted to a single task.
The temporal resolution of the attended channel
improves from
$\Delta t \sim N/B_{\text{PFC}}$
(multiplexing $N$ streams) to
$\Delta t \sim 1/B_{\text{PFC}}$ (single stream).
What folk psychology calls ``willpower'' is this
gating reallocation: a change in the
\emph{functional impedance}~$Z_{\text{fun}}$
(gate gains~$G_i$, arousal~$Z_{\text{arousal}}$),
not in the structural impedance~$Z_s$ that encodes
long-term patterns.
The subjective effort is real---the active
channel's $\Gamma^2 P_{\text{in}}$ at low~$T$
exceeds its cost at~$T_0$, and the $N-1$ silenced
channels surrender all fidelity---but the
\emph{structural} network is unchanged.
This is why ``willpower'' cannot rewrite deeply
forged patterns: gating redistributes bandwidth;
only C2 remodelling
($\Delta Z_s = -\eta\,\Gamma\,x_{\text{in}}\,x_{\text{out}}$)
can reshape the impedance itself
(Paper~3, Remark~4~\cite{Paper3};
Paper~4, Remark~3~\cite{Paper4}).
Paper~4 further decomposes effective willpower into
three multiplicative factors---metabolic budget
$\eta_{\text{pfc}}$, gate quality~$Q_{\text{gate}}$,
and memory calibration
$(1-\langle\Gamma^2_{\text{memory}}\rangle)$---so
that a single zero factor extinguishes volitional
capacity regardless of the other two~\cite{Paper4}.

The extreme case is emergency arousal.
In a car crash, the brainstem drives
$Z_{\text{arousal}}$ to its ceiling and the thalamus
gates every non-threat modality to zero.
The PFC processes a single high-$K$ stream
at maximum bandwidth; temporal resolution increases
by a factor~$\sim\!N$
and the event is perceived in \emph{slow motion}---not
an illusion, but a real $N$-fold increase in sampling
rate (Paper~4, Theorem~1~\cite{Paper4}).
Conversely, fatigue and cold \emph{reduce}~$B_{\text{PFC}}$
(higher~$\Gamma^2$), so fewer ``frames'' are processed
per second and time feels faster---the well-known
subjective acceleration of uneventful cold afternoons.

\subsection{Emergence classification}
\label{sec:emergence}

The operational status of every disease model in the codebase
is classified by \emph{emergence level}:

\begin{center}
\begin{tabular}{cll}
\hline
\textbf{Level} & \textbf{Name} & \textbf{Definition} \\
\hline
E0 & True Emergence & Only C1/C2/C3 + initial conditions. \\
   &                & Zero disease-specific code.         \\
E1 & Parameterised  & C2 via \texttt{ImpedanceChannel.remodel()} \\
   &                & but requires per-disease params.    \\
E2 & Scripted       & Ad-hoc $Z$ updates. Legacy only.    \\
\hline
\end{tabular}
\end{center}

\noindent
\textbf{Rule}: all new disease models must be E1 or higher.
E2 is forbidden for new code.
E0 is the target: if behaviour emerges from C2 + initial
conditions alone, no additional parameters should be added.

The tissue blueprints are E0 by construction:
the \texttt{GammaTopology} enforces C1 at every edge,
applies C2 remodeling at every tick,
and the only inputs are the initial $Z$-vectors and
the perturbation (impedance shift or edge removal).

Source code:
\texttt{alice/body/tissue\_blueprint.py}
(29~factory functions in \texttt{BLUEPRINT\_REGISTRY}),
\texttt{tests/test\_tissue\_blueprints.py}
(245~parametrised tests covering structure, C1, C2, and
organ-specific physiology for all 29~blueprints),
plus the original
\texttt{tests/test\_e0\_cardiovascular.py} (13~tests) and
\texttt{tests/test\_e0\_neural.py} (17~tests).
All 275~blueprint tests pass with 100\% rate.


% ============================================================
%  SECTION 10 — SCOPE EXCLUSION
% ============================================================
\section{What This Theory Does Not Claim}
\label{sec:scope}

The $\Gamma$-framework derives \emph{physical constraints}
that any living system must satisfy.
It does \emph{not} reconstruct evolutionary history.
Specifically:

\begin{enumerate}
  \item \textbf{Necessary conditions, not sufficient causes.}
    The framework shows that a $K{=}5$ brain \emph{must}
    maintain $T > T_c(5)$, \emph{must} have vasculature,
    and \emph{must} seek thermal shelter during sleep.
    It does not explain \emph{why} such brains appeared
    or \emph{which} lineages developed them.
  \item \textbf{No evolutionary trajectory.}
    Statements such as ``the tidal zone offers the
    lowest-action path'' identify geometric optima
    in impedance space.
    Whether any lineage actually traversed that path
    is a question for palaeontology and phylogenetics,
    not for this framework.
  \item \textbf{C2 uniqueness is mathematical, not biological.}
    The proof that C2 is the unique first-order
    $\mathcal{A}$-minimising rule (Paper~5) is a theorem
    about gradient descent.
    That multiple molecular machineries converge on the
    same equation is \emph{consistent with} C2 being a
    physical attractor; it is not evidence that evolution
    ``discovered'' C2.
  \item \textbf{Compatibility, not replacement.}
    Natural selection determines which lineages survive;
    the $\Gamma$-framework supplies the physical objective
    function that selection operates on.
    The two are complementary, not competing.
\end{enumerate}

\noindent
Throughout the six papers, any sentence referencing
evolution, convergence, or the Cambrian radiation
should be read as \emph{physical constraint language}:
``$X$ is required'' means ``any system with property~$Y$
must satisfy~$X$\,''; it does not mean ``$X$ evolved
because of~$Y$\,''.


% ============================================================
%  SECTION 11 — NOTATION
% ============================================================
\section{Notation Conventions}
\label{sec:notation}

\begin{itemize}
  \item $Z$: impedance (effort/flow ratio). Units depend on
    medium: $\Omega$ (electrical), Pa$\cdot$s/m$^3$ (vascular),
    N$\cdot$s/m (mechanical).
  \item $\Gamma$: dimensionless, $\in [-1, +1]$.
  \item $\eta$: remodeling rate, $> 0$. Tissue-dependent;
    $\eta \approx 0$ for cartilage (C2 null case).
  \item $(x_{\text{in}}, x_{\text{out}})$: generic input and
    output signals at an interface.  Replaces the earlier
    $(x_{\text{pre}}, x_{\text{post}})$ notation.
  \item $D_Z$: impedance debt, units of energy $\times$ time
    (J$\cdot$s).
  \item $H$: dimensionless, $\in [0, 1]$. Higher is healthier.
\end{itemize}


% ============================================================
%  SECTION 12 — CONCLUSION
% ============================================================
\section{Conclusion}
\label{sec:conclusion}

The $\Gamma$-Net framework rests on one variational
principle (MRP) and three local constraints
(C1: energy conservation; C2: impedance remodeling;
C3: impedance-tagged transport).
From these, five companion papers derive topology,
organ health, temporal dynamics, consciousness, and
clinical diagnostics---spanning 15 orders of spatial
magnitude and 29 tissue types, now unified into a
single whole-body topology (278~nodes, 426~edges)
through vascular and neural inter-organ buses,
with a rigorous thermoregulation derivation
showing that endothermy is a $\Gamma$-topological necessity
for brains above a critical modal complexity~$K$.

This paper provides the master reference:
a canonical quantity list (Table~\ref{tab:quantities}),
a verification matrix distinguishing internal from
external evidence (Table~\ref{tab:vv}),
and a falsifiable prediction roadmap
(Table~\ref{tab:predictions}).

All source code, simulation scripts, and NHANES pipelines
are available at
\url{https://github.com/cyhuang76/alice-gamma-net}
under AGPL-3.0.
The full test suite comprises 3{,}796 automated tests
with 100\% pass rate.


% ============================================================
%  BIBLIOGRAPHY
% ============================================================
\begin{thebibliography}{99}

\bibitem{Paper1}
H.-Y.~Huang,
``Topology and fractal cost of $\Gamma$-networks:
relay nodes, metabolic scaling, and the irreducibility
theorem,''
companion Paper~1 (2026).

\bibitem{Paper2}
H.-Y.~Huang,
``Dual-network organ health: vascular $\Gamma$-physics
and the five failure modes,''
companion Paper~2 (2026).

\bibitem{Paper3}
H.-Y.~Huang,
``Temporal dynamics of impedance debt: sleep, the lifecycle
equation, and the physics of aging,''
companion Paper~3 (2026).

\bibitem{Paper4}
H.-Y.~Huang,
``Memory, consciousness, and nociception as impedance
dynamics,''
companion Paper~4 (2026).

\bibitem{Paper5}
H.-Y.~Huang,
``The grand unification: $\Gamma$ as the universal interface
law from microtubules to power grids, and C2 as universal
remodeling in twenty-nine tissues,''
companion Paper~5 (2026).

\bibitem{ALICE_code}
H.-Y.~Huang,
\emph{ALICE: A physics-driven electronic lifeform},
\url{https://github.com/cyhuang76/alice-gamma-net} (2026).

\bibitem{PMC6674705}
H.~Carey, M.~Andrews, and S.~Martin,
``Mammalian hibernation: cellular and molecular responses to
depressed metabolism and low temperature,''
\emph{Physiol.\ Rev.} \textbf{83}, 1153 (2003);
see also PMC6674705.

\bibitem{PMC6629779}
S.~Giroud \emph{et~al.},
``The torpid state: recent advances in metabolic adaptations
and protective mechanisms,''
\emph{Front.\ Physiol.} \textbf{11}, 623 (2020);
PMC6629779.

\bibitem{PMC11880559}
F.~Seebacher,
``The evolution of metabolic regulation in animals,''
\emph{Comp.\ Biochem.\ Physiol.\ B} \textbf{224}, 207 (2024);
PMC11880559.

\bibitem{PMC12625846}
J.~K.~O'Brien \emph{et~al.},
``Body temperature, brain size, and the scaling of neural
complexity across vertebrates,''
\emph{Proc.\ R.\ Soc.\ B} (2025);
PMC12625846.

\bibitem{PMC7907648}
A.~Yu \emph{et~al.},
``Brain size is predicted by the intensity of intrasexual
competition in birds,''
\emph{Ecol.\ Evol.} \textbf{11}, 2652 (2021);
PMC7907648.

\end{thebibliography}

\end{document}
